Dispersion Distance and the Matter Distribution of the Universe in Dispersion Space

### 2015-07-30 writeup/referee_response.txt

We thank the review for the helpful suggestions and positive review. 
In the revised version of the manuscript, changes are highlighted in blue for
the reviewers and editor's convenience. Our responses to each of the reviewers
comments are in-line below.

@@

This was chosen to be roughly the value for star forming galaxies at these
redshifts as measured by the WiggleZ survey. The assumption here is that FRBs
might trace star formation, although this is entirely speculative. It also
provides some contrast with the electrons, since some terms are proportional to
b_e - b_f. This is now stated in the text.

> Also, it would be good to discuss briefly (perhaps
> with a new plot) the dependence of the paper’s conclusions on the
> value of b_f. In principle, variations of b_f could cause interesting
> effects, since b_f affects some of the terms but not others in Eq.
> (22). My guess is that the effects won’t be too big, since Fig. 2
> shows that the integral term is the dominant contribution, but it’d be
> nice to numerically confirm this. If anything, it would be helpful to
> know that the predictions are robust to uncertainties in b_f.

This was a very helpful comment and led us to include a b_f=0.7 line in Figure
3. We conclude that the sensitivity is indeed dominated by the integral term
and that a survey with 10000 events is unlikely to distinguish any signature of
the intrinsic clustering.

Time dependence of b_f should similarly be a small effect on the final
sensitivity. We've added a paragraph about the affect of the biases on the
various terms in the modelling section.

### 2015-07-30 writeup/dm_space_distortions.tex
Change to bias answer.

\blue{
The amplitude of the local and cross terms depend on the difference
between the electron bias and highly uncertain FRB bias
and the sign of the cross term depends on
which of these is larger. However, since the
integral term dominates for most radial distance pairs, our final sensitivity
estimates are largely unaffected by this uncertainty (as shown below). In a
high-precision survey the sensitivity of the cross and local terms to the
difference in the biases may help break measurement degeneracies between terms.
}

>>>>

\blue{
The amplitude of the local and cross terms depend on the difference
between the electron bias and highly uncertain FRB bias
and the sign of the cross term depends on
which of these is larger. However, since the
integral term dominates for most radial distance pairs, our final sensitivity
estimates are largely unaffected by this uncertainty (as shown below). In a
high-precision survey the sensitivity of the cross and local terms to the
difference in the biases may help break measurement degeneracies.
}
